### 2009-04-28 doc/tech_doc/storage_system/ARCStorage_src/Storagepaper-llncs.tex
Reorganizing doc catalogue and enabling make doc

A Grid storage system provides its clients with access to data
stored at remote storage systems. A traditional architecture (see
e.g. \cite{datagrid,egeeddm}) typically
consists of an {\it indexing service}, indexing files from storage
resources, a {\it replication service} for managing replica locations,
and a (often centralized) {\it metadata catalog} imposing a global
namespace on top of the resources. Data access can be handled either
through a file transfer service or directly through the storage
resource by quering the metadata catalog.

While this architecture has strongly improved the accessability of
physically distributed data, common Grid storage solutions typically have
some limitations: The metadata catalog, which is in most cases
centralized can quickly become a bottleneck. In typical Grid storage
systems, the storage resource is unaware of the state of its files,
making consistency guarantees hard to give. Traditional Grid
solutions often take for granted that the resource are dedicated for
the Grid, and in some cases even require specific operating systems,
thus restricting the amount of available hardware resources\footnote{It is often hard to convince a
system administrator to install a specific operating system to be able to share
her/his hardware resources in a Grid.}. In addition, lack of
standardization often makes interoperability between storage systems
non-trivial.
The NorduGrid Storage has as a goal to meet these limitations to
provide a truly distributed, self-healing, flexible Grid storage
solution, with a replicated metadata catalog, state aware storage
resources and an operating system agnostic implementation.
%/jon

\section{Related Work}
\label{Related Work}
%jon
Many Grid projects have developed their own, aplication specific
solutions. However, some general Grid storage solutions are widely
adopted:

dCache~\cite{dCache} is a service oriented storage system which combines heterogeneous storage
elements to collect several hundreds of terabytes in a single
namespace. Originally designed to work on a local area network,
dCache has proven to be usefull also in a Grid environment, with the
NDGF (Nordic Data Grid Facillity) dCache
installation~\cite{DSSWithdCache} as the largest example. There, the
core components, such as the metadata catalog, indexing service and
protocol doors are run in a centralized manner, while the storage
pools are distributed. The
NorduGrid storage, designed to have multiple instances of all
services running in a Grid environment, will not need a centralized
set of core services. Additionally, dCache is relatively difficult to
deploy and integrate with new applications. Being a more light-weight and flexible
storage solution, the NorduGrid storage aims more towards new user
groups less familiar with Grid solutions.

%% dCache~\cite{dCache} is a storage system which combines heterogeneous storage
%% elements to collect several hundreds of terabytes in a single
%% namespace. %% It additionally supports standard and native
%% protocols like gridftp, srm, dcap and gsidcap.
%jon
%dCache is
%a joint effort between Deutsches Elektronen Synchrotron (DESY) \cite{dCachesite}, Fermi National Accelerator Laboratory \cite{FermiLab}, the  Nordic Data
%Grid Facility (NDGF) \cite{NDGF}  and several other collaborators. %% The services or
%% components of dCache are known as cells. The standard deployment of
%% dCache consist of  storage pools; used to store file, optionally be
%% connected with HSM\footnote{Hierarchical Storage Manager, used for the
%%   tape storage}. Namespace manager; used PNFS \footnote{Perfectly
%%   Normal FileSystem; A network file system, designed in Desy} as a
%% filesystem  for storing matadata. And the number of protocol
%% doors. One of the biggest deployment of dCache is the distributed
%% infrastructure of  NDGF.\\ 
%% dCache has proven to be a fairly stable and scalable solution. However,
%% it is relatively difficult to deploy and integrate with new applications. 
%% The NorduGrid storage, being a light-weight and flexible
%% storage solution, aims more towards new user groups less familiar with
%% Grid solutions. 
%jon
%% \textbf{BigTable:} Bigtable is a distributed storage system managing structured data on
%% the petabyte-scale \cite{Bigtable}. It is currently used within
%% Google in projects such as web indexing, Google Earth and Google
%% Financing. %% Bigtable is mainly built on top of three pieces of Google's
%% %% infrastructure: The Google Filesystem \cite{GFS} a distributed,
%% %% replicating file system, the Google SSTable, providing
%% %% a persistent, ordered immutable map and Chubby \cite{Chubby}, a highly
%% %% available and persistent distributed lock service. The system uses a
%% %% three-level B$^+$-tree to store \textit{tablets}. The location of the
%% %% first level is stored in Chubby, making Chubby a vitaly important part
%% %% of the design. To ensure a persistent solution, Chubby takes advantage
%% %% of the Paxos algorithm \cite{Paxos,PaxosLive}.\\
%% Bigtable has several interesting features, one of which is the
%% distributed lock service, Chubby \cite{Chubby}. Chubby is a high-availability, distributed
%% locking service sitting on top of the B$^+$-tree architecture of
%% Bigtable. Chubby has several features similar to our A-Hash service, %(see Section \ref{Hash Algorithm}),
%% among which the use of the Paxos algorithm \cite{Paxos,PaxosLive}, is
%% the most striking. A major caveat for the Grid community is that
%% Bigtable is neither free, open-source nor available to the public.
%jon

@@

Based on the client-server model,
the Storage Resource Broker (SRB) \cite{earlySRB,SRB} provides a flexible data grid management
system. It allows  uniform access to heterogeneous
storage resources over a wide area network. %% SRB also manages the
%% namespaces used to identify files, storage resources, users, metadata,
%% and access controls independently of the physical storage systems. It
%% uses centralized matadata catalog (MCat). Also supports several file
%% systems of UNIX, Windows, Linux, Mac OS X, HPSS and large scale
%% storage systems like Castor and dCache.\\
Its functionality, with a uniform namespace for several Data Grid
Managers and file systems, is quite similar to the functionality
offered by our Gateway service (see Section \ref{Features}). However, being built as a middleware on top of
other major storage solutions, SRB does not offer its own storage solution.

@@

\item The \textbf{A-Hash}  %A-Hash 
is a hash table for consistently storing data in property-value
pairs. All metadata about files, collections, mount point, Shepherd's
health status, and so forth, is stored in the A-Hash. As the A-Hash is
the service storing the entire state of the storage system, it is
absolutely crucial for the sttorage system that the A-Hash is
consistent. The distribution and replication of this service is
therefore both necessary and challenging.

@@

\item \textbf{Fault tolerance:} Due to the unpredictable nature of the Grid environment, it is essential to
have some degree of  automatic recovery system in case of unexpected
failures. Fault tolerant behavior is required both at the level of
metadata and on the level of physical storage. While the work on fault-tolerant metadata is still in
progress, the following two
scenarios will explain the currently available recovery mechanism for
physical storage: 
\begin{itemize}
\item In the case of a file having an invalid checksum, the Shepherd
immediately informs the Librarian and the Librarian changes the state of the given replica to
`\textbf{invalid}'. To recover its replica, the Shepherd contacts a
Bartender and asks for another replica of the file. The Bartender chooses a valid
replica, initiates a file transfer from a Shepherd having the replica,
and returns the TURL to the Shepherd with the invalid replica. When the
Shepherd has received the replica and compared the checksum, it notifies the
Librarian that the replica is alive again.  
\item In the case of a Shepherd going offline, a Librarian will,
  as mentioned earlier, notice the lack of heartbeats and invalidate all the
  replicas, initiating new replication for all the files stored in
  this storage node. However, if the Shepherd
  again comes online, there will evidently be more replicas than
  needed. The first Shepherd to notice this will set its replica's
  state to `\textbf{thirdwheel}', i.e. obsolete. At the next occasion,
  the Shepherd will remove the replica, if and only if it has the only
  `\textbf{thirdwheel}' replica of this file. If there are more
  replicas with this state, all replicas will be set back to
  `\textbf{alive}' and the process is repeated. This scenario will be discussed further in Section
  \ref{Testing and Discussion}.
\end{itemize}

@@

As is the case for all openly accessible web services, the security
model is of crucial importance for the NorduGrid storage. The security
architecture of the storage can be split into three parts; the
inter-service authorization; the transfer-level authorization; and the
high-level authorization:
\begin{itemize}
\item The \textbf{inter-service authorization} maintains the integrity of the
  internal communication between services. There are several
  communication paths between the services in the storage system. The
  Bartenders send requests to the Librarians and the Shepherds, the
  Shepherds communicate with the Librarians and the Librarians talk with
  the A-Hash. If any of these services is compromised or a new
  rogue service gets inserted in the system, the security of the
  entire system is compromised. To enable trust between the services,
  they need to know each other's Distinguished Names (DNs). This way,
  a rogue service would need to obtain a certificate with that exact
  DN from some trusted Certificate Authority (CA).
\item The \textbf{transfer-level authorization} handles the
  authorization in the cases of uploading and downloading files. When
  a transfer is requested, the Shepherd will provide a one-time
  Transfer URL (TURL) to which the client can connect. In the
  current architecture, this TURL is world-accessible. This may not seem
  very secure at first. However, provided that the TURL has a very long,
  unguessable name, that it is transfered to the user in a secure way
  and that it can only be accessed once before it is deleted, the
  chance of being compromized is very low.
\item The \textbf{high-level authorization} considers the access
  policies for the files and collections in the system. These policies
  are stored in A-Hash, in the metadata of the corresponding file or
  collection, providing a fine-grained security in the system.
\end{itemize}
The communication with and within the storage system is realized
through HTTPS with standard X.509 authentication.

@@

The following tests were carried out:
\begin{itemize}
\item \textbf{Test 1:} The distribution of data after uploading 10 large size (1 GB)
  files with one replica each.  
\item \textbf{Test 2:} The distribution of files after uploading 100 small size (1 kB)
  files with one replica each, and with simultanious uploading.
\item \textbf{Test 3:} The distribution of data after repeating Tests 1 and 2 with three replicas.  
\item \textbf{Test 4:} System behavior while some of the Shepherds are offline.   
\end{itemize}

@@

A significant feature of the NorduGrid storage is its automatic self-healing. Test 4 addresses this feature by studying the effect of
taking one Shepherd out of the system, and later reinserting it. Table
\ref{table:self healing} shows the storage distribution in three
states: Before interrupting a Shepherd, after the USIT-2
Shepherd is interrupted and redistribution of replicas is finished, and
alive, when the Shepherd is restarted and the system again has stabilized. We
can see that all files are properly distributed between the remaining
Shepherds when one of them is disrupted and that the storage load evens out 
again when the Shepherd comes back online. When the
system discovers that there are more replicas than needed, the first
Shepherd noticing will set mark its replica as obsolete. Since the failing Shepherd didn't lose any replicas while
being down, redistribution of replicas is just a matter of deleting
obsolete replicas. We also see that the NIIF node actually got fewer
files when USIT-2 went offline. If two Shepherds simultaneously
start uploading and replicating a missing replica, there will be too many
replicas. Here, a big replica on the NIIF node has randomly been chosen as
obsolete. However, the total storage usage remains the same in all
three cases.

>>>>

A Grid storage system provides its clients with access to data
stored at remote storage systems. A traditional architecture (see
e.g. \cite{datagrid,egeeddm}) typically
consists of an {\it indexing service}, indexing files from storage
resources, a {\it replication service} for managing replica locations,
and a (often centralized) {\it metadata catalog} imposing a global
namespace on top of the resources. Data access can be handled either
through a file transfer service or directly through the storage
resource by querying the metadata catalog.

While this architecture has strongly improved the accessibility of
physically distributed data, common Grid storage solutions typically have
some limitations: The metadata catalog, which is in most cases
centralized can quickly become a bottleneck. In typical Grid storage
systems, the storage resource is unaware of the state of its files,
making consistency guarantees hard to give. Traditional Grid
solutions often take for granted that the resources are dedicated for
the Grid, and in some cases even require specific operating systems,
thus restricting the amount of available hardware resources\footnote{It is often hard to convince a
system administrator to install a specific operating system to be able to share
her/his hardware resources in a Grid.}. In addition, lack of
standardization often makes interoperability between storage systems
non-trivial.
The NorduGrid Storage has as a goal to meet these limitations to
provide a truly distributed, self-healing, flexible Grid storage
solution, with a replicated metadata catalog, state aware storage
resources and an operating system agnostic implementation.
%/jon

\section{Related Work}
\label{Related Work}
%jon
Many Grid projects have developed their own, application specific
solutions. However, some general Grid storage solutions are widely
adopted:

dCache~\cite{dCache} is a service oriented storage system which combines heterogeneous storage
elements to collect several hundreds of terabytes in a single
namespace. Originally designed to work on a local area network,
dCache has proven to be useful also in a Grid environment, with the
NDGF (Nordic Data Grid Facility) dCache
installation~\cite{DSSWithdCache} as the largest example. There, the
core components, such as the metadata catalog, indexing service and
protocol doors are run in a centralized manner, while the storage
pools are distributed. The
NorduGrid storage, designed to have multiple instances of all
services running in a Grid environment, will not need a centralized
set of core services. Additionally, dCache is relatively difficult to
deploy and integrate with new applications. Being a more light-weight and flexible
storage solution, the NorduGrid storage aims more towards new user
groups less familiar with Grid solutions.

%% dCache~\cite{dCache} is a storage system which combines heterogeneous storage
%% elements to collect several hundreds of terabytes in a single
%% namespace. %% It additionally supports standard and native
%% protocols like gridftp, srm, dcap and gsidcap.
%jon
%dCache is
%a joint effort between Deutsches Elektronen Synchrotron (DESY) \cite{dCachesite}, Fermi National Accelerator Laboratory \cite{FermiLab}, the  Nordic Data
%Grid Facility (NDGF) \cite{NDGF}  and several other collaborators. %% The services or
%% components of dCache are known as cells. The standard deployment of
%% dCache consist of  storage pools; used to store file, optionally be
%% connected with HSM\footnote{Hierarchical Storage Manager, used for the
%%   tape storage}. Namespace manager; used PNFS \footnote{Perfectly
%%   Normal FileSystem; A network file system, designed in Desy} as a
%% filesystem  for storing metadata. And the number of protocol
%% doors. One of the biggest deployment of dCache is the distributed
%% infrastructure of  NDGF.\\ 
%% dCache has proven to be a fairly stable and scalable solution. However,
%% it is relatively difficult to deploy and integrate with new applications. 
%% The NorduGrid storage, being a light-weight and flexible
%% storage solution, aims more towards new user groups less familiar with
%% Grid solutions. 
%jon
%% \textbf{BigTable:} Bigtable is a distributed storage system managing structured data on
%% the petabyte-scale \cite{Bigtable}. It is currently used within
%% Google in projects such as web indexing, Google Earth and Google
%% Financing. %% Bigtable is mainly built on top of three pieces of Google's
%% %% infrastructure: The Google Filesystem \cite{GFS} a distributed,
%% %% replicating file system, the Google SSTable, providing
%% %% a persistent, ordered immutable map and Chubby \cite{Chubby}, a highly
%% %% available and persistent distributed lock service. The system uses a
%% %% three-level B$^+$-tree to store \textit{tablets}. The location of the
%% %% first level is stored in Chubby, making Chubby a vitally important part
%% %% of the design. To ensure a persistent solution, Chubby takes advantage
%% %% of the Paxos algorithm \cite{Paxos,PaxosLive}.\\
%% Bigtable has several interesting features, one of which is the
%% distributed lock service, Chubby \cite{Chubby}. Chubby is a high-availability, distributed
%% locking service sitting on top of the B$^+$-tree architecture of
%% Bigtable. Chubby has several features similar to our A-Hash service, %(see Section \ref{Hash Algorithm}),
%% among which the use of the Paxos algorithm \cite{Paxos,PaxosLive}, is
%% the most striking. A major caveat for the Grid community is that
%% Bigtable is neither free, open-source nor available to the public.
%jon

@@

Based on the client-server model,
the Storage Resource Broker (SRB) \cite{earlySRB,SRB} provides a flexible data grid management
system. It allows  uniform access to heterogeneous
storage resources over a wide area network. %% SRB also manages the
%% namespaces used to identify files, storage resources, users, metadata,
%% and access controls independently of the physical storage systems. It
%% uses centralized metadata catalog (MCat). Also supports several file
%% systems of UNIX, Windows, Linux, Mac OS X, HPSS and large scale
%% storage systems like Castor and dCache.\\
Its functionality, with a uniform namespace for several Data Grid
Managers and file systems, is quite similar to the functionality
offered by our Gateway service (see Section \ref{Features}). However, being built as a middleware on top of
other major storage solutions, SRB does not offer its own storage solution.

@@

\item The \textbf{A-Hash}  %A-Hash 
is a hash table for consistently storing data in property-value
pairs. All metadata about files, collections, mount point, Shepherd's
health status, and so forth, is stored in the A-Hash. As the A-Hash is
the service storing the entire state of the storage system, it is
absolutely crucial for the storage system that the A-Hash is
consistent. The distribution and replication of this service is
therefore both necessary and challenging.

@@

\item \textbf{Fault tolerance:} Due to the unpredictable nature of the Grid environment, it is essential to
have some degree of  automatic recovery system in case of unexpected
failures. Fault tolerant behavior is required both at the level of
metadata and on the level of physical storage. While the work on fault-tolerant metadata is still in
progress, the following two
scenarios will explain the currently available recovery mechanism for
physical storage: 
\begin{itemize}
\item In the case of a file having an invalid checksum, the Shepherd
immediately informs the Librarian and the Librarian changes the state of the given replica to
`\textbf{invalid}'. To recover its replica, the Shepherd contacts a
Bartender and asks for another replica of the file. The Bartender chooses a valid
replica, initiates a file transfer from a Shepherd having the replica,
and returns a Transfer URL to the Shepherd with the invalid replica. When the
Shepherd has received the replica and compared the checksum, it notifies the
Librarian that the replica is alive again.  
\item In the case of a Shepherd going offline, a Librarian will,
  as mentioned earlier, notice the lack of heartbeats and invalidate all the
  replicas, initiating new replication for all the files stored in
  this storage node. However, if the Shepherd
  again comes online, there will evidently be more replicas than
  needed. The first Shepherd to notice this will set its replica's
  state to `\textbf{thirdwheel}', i.e. obsolete. At the next occasion,
  the Shepherd will remove the replica, if and only if it has the only
  `\textbf{thirdwheel}' replica of this file. If there are more
  replicas with this state, all replicas will be set back to
  `\textbf{alive}' and the process is repeated. This scenario will be discussed further in Section
  \ref{Testing and Discussion}.
\end{itemize}

@@

As is the case for all openly accessible web services, the security
model is of crucial importance for the NorduGrid storage. The security
architecture of the storage can be split into three parts; the
inter-service authorization; the transfer-level authorization; and the
high-level authorization:
\begin{itemize}
\item The \textbf{inter-service authorization} maintains the integrity of the
  internal communication between services. There are several
  communication paths between the services in the storage system. The
  Bartenders send requests to the Librarians and the Shepherds, the
  Shepherds communicate with the Librarians and the Librarians talk with
  the A-Hash. If any of these services is compromised or a new
  rogue service gets inserted in the system, the security of the
  entire system is compromised. To enable trust between the services,
  they need to know each other's Distinguished Names (DNs). This way,
  a rogue service would need to obtain a certificate with that exact
  DN from some trusted Certificate Authority (CA).
\item The \textbf{transfer-level authorization} handles the
  authorization in the cases of uploading and downloading files. When
  a transfer is requested, the Shepherd will provide a one-time
  Transfer URL (TURL) to which the client can connect. In the
  current architecture, this TURL is world-accessible. This may not seem
  very secure at first. However, provided that the TURL has a very long,
  unguessable name, that it is transfered to the user in a secure way
  and that it can only be accessed once before it is deleted, the
  chance of being compromised is very low.
\item The \textbf{high-level authorization} considers the access
  policies for the files and collections in the system. These policies
  are stored in A-Hash, in the metadata of the corresponding file or
  collection, providing a fine-grained security in the system.
\end{itemize}
The communication with and within the storage system is realized
through HTTPS with standard X.509 authentication.

@@

The following tests were carried out:
\begin{itemize}
\item \textbf{Test 1:} The distribution of data after uploading 10 large size (1 GB)
  files with one replica each.  
\item \textbf{Test 2:} The distribution of files after uploading 100 small size (1 kB)
  files with one replica each, and with simultaneous uploading.
\item \textbf{Test 3:} The distribution of data after repeating Tests 1 and 2 with three replicas.  
\item \textbf{Test 4:} System behavior while some of the Shepherds are offline.   
\end{itemize}

@@

A significant feature of the NorduGrid storage is its automatic self-healing. Test 4 addresses this feature by studying the effect of
taking one Shepherd out of the system, and later reinserting it. Table
\ref{table:self healing} shows the storage distribution in three
states: Before interrupting a Shepherd, after the USIT-2
Shepherd is interrupted and redistribution of replicas is finished, and
alive, when the Shepherd is restarted and the system again has stabilized. We
can see that all files are properly distributed between the remaining
Shepherds when one of them is disrupted and that the storage load evens out 
again when the Shepherd comes back online. When the
system discovers that there are more replicas than needed, the first
Shepherd noticing will set mark its replica as obsolete. Since the failing Shepherd did not lose any replicas while
being down, redistribution of replicas is just a matter of deleting
obsolete replicas. We also see that the NIIF node actually got fewer
files when USIT-2 went offline. If two Shepherds simultaneously
start uploading and replicating a missing replica, there will be too many
replicas. Here, a big replica on the NIIF node has randomly been chosen as
obsolete. However, the total storage usage remains the same in all
three cases.

### 2009-04-28 doc/tech_doc/storage_system/arc-storage-documentation.tex
Reorganizing doc catalogue and enabling make doc

In addition to the Logical Names we can refer to a file or collection simply by its GUID, or we can use GUID's and Logical Names together, as seen in Figure~\ref{fig:namespace}.

@@

An example of the hierarchy of the global namespace is shown in Figure~\ref{fig:namespace}: if we have a collection with GUID \verb#1234#, and there is a collection called \verb#green# in it, and in \verb#green# there is another collection called \verb#orange#, and in \verb#orange# there is a file called \verb#huge#, then we can refer to this file with the Logical Name \verb#1234/green/orange/huge#, which means that from the collection called \verb!1234! we have to follow along the path: \verb!green!, \verb!orange!, \verb!huge!.

@@

Chelonia consists of several services (both different kinds of services and multiple instances of the same kind). The A-Hash, Librarian and Shepherd services are `internal' services in the sense that the end-user of the storage system never communicates with them directly. But these internal services are communicating with each other, thus they have to know which other services to trust. We call this aspect of the security architecture of Chelonia `inter-service authorization'.

@@

Besides specifying only one user with a DN, there are other types of access control rules: we can have a rule for a whole VO (Virtual Organization) or for all users, like this:

@@

Currently the transfer-level authorization is very simple. When the Bartender decides that a user has permission to download a file, then the Bartender chooses a replica, and initiates the transfer. The result of this initiation is the transfer URL (TURL). This TURL is unique for each request, even for requests for the same replica, and this TURL is only valid for one download. Currently we configure the storage element services to not do any authorization, and we use these one-time TURL's to ensure that only authorized users can access the contents of the storage elements.

@@

\begin{enumerate}
    \item The client tool contacts a Bartender and send a `makeCollection' request with the LN \verb!/ourvo/common/docs!.
    \item The Bartender asks a Librarian to traverse this LN.
    \item The Librarian tries to traverse the Logical Name and it stops at the last possible point and returns the metadata of the last element. Because the user wants to put his collection in a new path but into an existing collection, we expect that only the \verb#/ourvo/common# part of the LN can be traversed. If the Librarian can traverse the whole LN it means that there is already an existing file or collection by that name. If LN does not exist but the the parent collection does, then the parent collection's metadata is returned to the Bartender. 
    \item The Bartender checks the access policies to decide if the user has permissions to put something into this collection. Then it asks the Librarian to create a new collection.
    \item The Librarian creates the collection, and returns its GUID. At this point this new collection has no real Logical Name, it only has a GUID, but it is not yet put into its parent collection.
    \item The Bartender now asks the Librarian to add this new entry into the parent collection, which means that the new GUID and the name \verb!docs! are added as a pair.
    \item The Librarian returns with a status message.
    \item Finally the Bartender tells the client tool if everything went OK or not.
\end{enumerate}

@@

The Librarian services use the A-Hash services to store the metadata, using the GUID's as unique ID's. For this, we have to represent the metadata as property-value pairs organized in section. The files, the collections and the mount points have some common attributes: the GUID, the type and the owner which are in the \emph{entry} section; the creation and modification timestamps in the \emph{timestamps} section, a list of access control rules in the \emph{policy} section; the list of parent collections where this entry has a `hardlink' in the \emph{parents} section; and optional, arbitrary property-value pairs in the \emph{metadata} section.

@@

A file in Chelonia has a logical entry in the namespace, and one or more physical replicas on the storage nodes. We store the locations of the replicas in the \emph{locations} section. A location contains the URL of the Shepherd service, the local ID of the file within the storage node and the state of the replica. This state is `\textbf{alive}' if the replica passed the checksum test, and the Shepherd reports that the storage node is healthy, `\textbf{invalid}' if the replica has wrong checksum, or the Shepherd claims it has no such file, `\textbf{offline}' if the Shepherd is not reachable, but may have a valid replica, `\textbf{creating}' if the replica is in the state of uploading, `\textbf{thirdwheel}' if the replica is marked for deletion because of too many replicas, or `\textbf{stalled}' if the the replica was in the state of uploading for a long time but hasn't arrived. The \emph{states} section contains the size of the file, the number of required replicas, and a checksum of the file, which is created by some kind of checksumming algorithm (currently only md5 is supported).

@@

A \emph{collection} is a list of files and other collections, which are in parent-children relationships forming a tree-like hierarchy (with possible interconnection due to hardlinks). Each entry has a unique name within a collection and a GUID which points to a corresponding file or collection, so a collection is basically a list of name-GUID pairs, which list is stored in the \emph{entries} section (see below). The collections can be in a closed state, which means that its contents should not be changed. If you close a collection then it cannot be opened again. However it cannot be guaranteed that the contents of a closed collection remains the same (e.g. if we include in our collection a file which we don't own, then the owner of the file can still remove it), but if a closed collection is changed, its state will be broken, and this state can never be changed again, which means you will always know if a closed collection is not intact anymore. This state is stored in the \emph{states} section, and its possible values are `\textbf{no}' if the collection is not closed, `\textbf{yes}' if the collection is closed and `\textbf{broken}' if the collection was closed, but something happened, and its contents have been changed.

@@

For inter-service authorization the services can be configured to only accept connections from trusted services. A service is trusted if we know its DN. For each service we can write trusted DN's in the configuration, or we can periodically get the list from an A-Hash. This can be configured with a `\emph{TrustManager}' section in the service configuration, which contains these entries:

@@

The TrustManager section itself have the following optional attributes: \textbf{FromFile} can specify a filename if we want to get the whole TrustManager configuration from a separate file; and \textbf{Force} indicates (with `yes' or `no', default: `yes') that we want to ensure that our service does not even get the request if the client of the incoming connection is not trusted.

@@

    The \emph{changeRequestList} is a list of \emph{changeRequest}s, where a \emph{changeRequest} is a tuple of (\emph{changeID}, \emph{ID}, \emph{changeType}, \emph{section}, \emph{property}, \emph{value}, \emph{conditionList}):
\begin{itemize}
\item \emph{changeID} is an arbitrary ID which is used in the response to refer to this part of the request
\item \emph{ID} points to the object we want to change
\item \emph{changeType} can be `\textbf{set}' to set the property within the section to value, `\textbf{unset}' to remove the property from the section regardless of the value, `\textbf{delete}' to remove the whole object
\item \emph{conditionList} is a list of \emph{condition}s, where a \emph{condition} is a tuple of (\emph{conditionID}, \emph{conditionType}, \emph{section}, \emph{property}, \emph{value}), where \emph{conditionType} can be `\textbf{is}' which will be true if the property in the section is set to the value, `\textbf{isnot}' which will be true if the property in the section is not set to the value, `\textbf{isset}' which will be true if the property of the section is set regardless of the value or `\textbf{unset}' which will be true if the property of the section is not set at all.
\end{itemize}
    If all conditions are met, the A-Hash tries to apply changes to the objects, and creates a new object if a previously non-existent ID is given.

@@

    The \emph{newRequestList} is a list of (\emph{requestID}, \emph{metadataList}) where \emph{requestID} is an arbitrary ID used to identify this request in the list of responses; \emph{metadataList} is a list of (\emph{section}, \emph{property}, \emph{value}) tuples.
    This method generates a \emph{GUID} for each request, and inserts the new entry (with the given metadata) into the A-Hash, then returns the GUID's of the newly created entries. In the metadata of the new entry the `type' property in the `entry' section defines whether it is a file, a collection or a mount point. The `GUID' property can contain a GUID if we want to specify the GUID of the new entry, and don't want the Librarian to generate a random one.

>>>>

In addition to the Logical Names a file or collection can be refered to simply by its GUID, or you can use GUID's and Logical Names together, as seen in Figure~\ref{fig:namespace}.

@@

An example of the hierarchy of the global namespace is shown in Figure~\ref{fig:namespace}: if you have a collection with GUID \verb#1234#, and there is a collection called \verb#green# in it, and in \verb#green# there is another collection called \verb#orange#, and in \verb#orange# there is a file called \verb#huge#, then you can refer to this file with the Logical Name \verb#1234/green/orange/huge#, which means that from the collection called \verb!1234! you have to follow along the path: \verb!green!, \verb!orange!, \verb!huge!.

@@

Chelonia consists of several services (both different kinds of services and multiple instances of the same kind). The A-Hash, Librarian and Shepherd services are `internal' services in the sense that the end-user of the storage system never communicates with them directly. But these internal services are communicating with each other, thus they have to know which other services to trust. This aspect of the security architecture of Chelonia is called `inter-service authorization'.

@@

Besides specifying only one user with a DN, there are other types of access control rules. For example, you can have a rule for a whole VO (Virtual Organization) or for all users, like this:

@@

Currently the transfer-level authorization is very simple. When the Bartender decides that a user has permission to download a file, then the Bartender chooses a replica, and initiates the transfer. The result of this initiation is the transfer URL (TURL). This TURL is unique for each request, even for requests for the same replica, and this TURL is only valid for one download. Currently the storage element services are  configured to not do any authorization, and these one-time TURL's are used to ensure that only authorized users can access the contents of the storage elements.

@@

\begin{enumerate}
    \item The client tool contacts a Bartender and send a `makeCollection' request with the LN \verb!/ourvo/common/docs!.
    \item The Bartender asks a Librarian to traverse this LN.
    \item The Librarian tries to traverse the Logical Name and it stops at the last possible point and returns the metadata of the last element. Because the user wants to put his collection in a new path but into an existing collection, only the \verb#/ourvo/common# part of the LN is expected to be traversed. If the Librarian can traverse the whole LN it means that there is already an existing file or collection by that name. If LN does not exist but the the parent collection does, then the parent collection's metadata is returned to the Bartender. 
    \item The Bartender checks the access policies to decide if the user has permissions to put something into this collection. Then it asks the Librarian to create a new collection.
    \item The Librarian creates the collection, and returns its GUID. At this point this new collection has no real Logical Name, it only has a GUID, but it is not yet put into its parent collection.
    \item The Bartender now asks the Librarian to add this new entry into the parent collection, which means that the new GUID and the name \verb!docs! are added as a pair.
    \item The Librarian returns with a status message.
    \item Finally the Bartender tells the client tool if everything went OK or not.
\end{enumerate}

@@

The Librarian services use the A-Hash services to store the metadata, using the GUID's as unique ID's. For this, the metadata have to be represented as property-value pairs organized in section. The files, the collections and the mount points have some common attributes: the GUID, the type and the owner which are in the \emph{entry} section; the creation and modification timestamps in the \emph{timestamps} section, a list of access control rules in the \emph{policy} section; the list of parent collections where this entry has a `hardlink' in the \emph{parents} section; and optional, arbitrary property-value pairs in the \emph{metadata} section.

@@

A file in Chelonia has a logical entry in the namespace, and one or more physical replicas on the storage nodes. The locations of the replicas have to be stored in the \emph{locations} section. A location contains the URL of the Shepherd service, the local ID of the file within the storage node and the state of the replica. This state is `\textbf{alive}' if the replica passed the checksum test, and the Shepherd reports that the storage node is healthy, `\textbf{invalid}' if the replica has wrong checksum, or the Shepherd claims it has no such file, `\textbf{offline}' if the Shepherd is not reachable, but may have a valid replica, `\textbf{creating}' if the replica is in the state of uploading, `\textbf{thirdwheel}' if the replica is marked for deletion because of too many replicas, or `\textbf{stalled}' if the the replica was in the state of uploading for a long time but hasn't arrived. The \emph{states} section contains the size of the file, the number of required replicas, and a checksum of the file, which is created by some kind of checksumming algorithm (currently only md5 is supported).

@@

A \emph{collection} is a list of files and other collections, which are in parent-children relationships forming a tree-like hierarchy (with possible interconnection due to hardlinks). Each entry has a unique name within a collection and a GUID which points to a corresponding file or collection, so a collection is basically a list of name-GUID pairs, which list is stored in the \emph{entries} section (see below). The collections can be in a closed state, which means that its contents should not be changed. If you close a collection then it cannot be opened again. However it cannot be guaranteed that the contents of a closed collection remains the same (e.g. if a user include in his collection a file which he does not own, then the owner of the file can still remove it), but if a closed collection is changed, its state will be broken, and this state can never be changed again, which means you will always know if a closed collection is not intact anymore. This state is stored in the \emph{states} section, and its possible values are `\textbf{no}' if the collection is not closed, `\textbf{yes}' if the collection is closed and `\textbf{broken}' if the collection was closed, but something happened, and its contents have been changed.

@@

For inter-service authorization the services can be configured to only accept connections from trusted services. A service is trusted if its DN is known. For each service the trusted DN's can be inserted to the configuration, or the list can periodically be retrieved from an A-Hash. This can be configured with a `\emph{TrustManager}' section in the service configuration, which contains these entries:

@@

The TrustManager section itself have the following optional attributes: \textbf{FromFile} can specify a filename if the whole TrustManager configuration should be taken from a separate file; and \textbf{Force} indicates (with `yes' or `no', default: `yes') that you want to ensure that your service does not even get the request if the client of the incoming connection is not trusted.

@@

    The \emph{changeRequestList} is a list of \emph{changeRequest}s, where a \emph{changeRequest} is a tuple of (\emph{changeID}, \emph{ID}, \emph{changeType}, \emph{section}, \emph{property}, \emph{value}, \emph{conditionList}):
\begin{itemize}
\item \emph{changeID} is an arbitrary ID which is used in the response to refer to this part of the request
\item \emph{ID} points to the object to be change
\item \emph{changeType} can be `\textbf{set}' to set the property within the section to value, `\textbf{unset}' to remove the property from the section regardless of the value, `\textbf{delete}' to remove the whole object
\item \emph{conditionList} is a list of \emph{condition}s, where a \emph{condition} is a tuple of (\emph{conditionID}, \emph{conditionType}, \emph{section}, \emph{property}, \emph{value}), where \emph{conditionType} can be `\textbf{is}' which will be true if the property in the section is set to the value, `\textbf{isnot}' which will be true if the property in the section is not set to the value, `\textbf{isset}' which will be true if the property of the section is set regardless of the value or `\textbf{unset}' which will be true if the property of the section is not set at all.
\end{itemize}
    If all conditions are met, the A-Hash tries to apply changes to the objects, and creates a new object if a previously non-existent ID is given.

@@

    The \emph{newRequestList} is a list of (\emph{requestID}, \emph{metadataList}) where \emph{requestID} is an arbitrary ID used to identify this request in the list of responses; \emph{metadataList} is a list of (\emph{section}, \emph{property}, \emph{value}) tuples.
    This method generates a \emph{GUID} for each request, and inserts the new entry (with the given metadata) into the A-Hash, then returns the GUID's of the newly created entries. In the metadata of the new entry the `type' property in the `entry' section defines whether it is a file, a collection or a mount point. The `GUID' property can contain a GUID if you want to specify the GUID of the new entry, and don't want the Librarian to generate a random one.
